Data_visualization

### 2018-08-31 Rmd/Data_visualization.Rmd
changes data_visualization plots with common names

\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae")
```
\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae")
```
\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae")
```

>>>>

\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))

```
\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))

```
\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))
